Qualitative Assessesment of Graph Neural Network Potentials for Phonon Properties of Shape Memory Alloys using Graph Neural Network Potentials

### 2024-02-04 src/tex/ms.tex
Dummy pay attention to file names. Does showyourwork make this easier to track.

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B2_ModelsPhononbandstructure.png}
		\caption{ Ground-state, no isotropic strain, Phonon bandstructure
			of B2 phase for all models. The Mutter and Zhong EAM potentials
			differ in that Mutter predicts no dynamic instability of the B2
			phase at 0K.  }
		\label{fig:allmodels_b2}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19_ModelsPhononbandstructure.png}
		\caption{ Ground-state phonon bandstructure of B19 phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19P_ModelsPhononbandstructure.png}
		\caption{ Ground-state phonon bandstructure of
			\textit{B19}$^\prime$ phase for all models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_BCO_ModelsPhononbandstructure.png}
		\caption{ Ground-state phonon bandstructure of BCO phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Mutter_B2_StrainsPhononbandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Zhong_B2_StrainsPhononbandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Ko_B2_StrainsPhononbandstructure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) EAM
			Mutter, (middle) EAM Zhong, and (bottom) 2NN-MEAM Ko potentials
			at different isotropic strains. The optical branches have been
			made more transparent to emphasis the behavior in the TA$_1$ and
			TA$_2$ branches. The color indicates direction from compressive
			to tensile strain. Note that the strain percent shown is with
			respect to isotropic changes (i.e. volume).  }
		\label{fig:mutter_zhong_ko_phonon_b2}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_M3GNet_B2_StrainsPhononband
			structure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_CHGNet_B2_StrainsPhononband
			structure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_MACE_B2_StrainsPhononband
			structure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) M3GNet,
			(middle) CHGNet, and (bottom) MACE potentials for different
			isotropic strains. Similar transcparency is used as done in
			\ref{fig:mutter_zhong_phonon_b2}.  }
		\label{fig:gnn_phonon_b2}
	\end{centering}
\end{figure}

>>>>

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B2_ModelsPhononBandstructure.png}
		\caption{ Ground-state, no isotropic strain, Phonon bandstructure
			of B2 phase for all models. The Mutter and Zhong EAM potentials
			differ in that Mutter predicts no dynamic instability of the B2
			phase at 0K.  }
		\label{fig:allmodels_b2}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of B19 phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19P_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of
			\textit{B19}$^\prime$ phase for all models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_BCO_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of BCO phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Mutter_B2_StrainsPhononbandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Zhong_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Ko_B2_StrainsPhononBandstructure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) EAM
			Mutter, (middle) EAM Zhong, and (bottom) 2NN-MEAM Ko potentials
			at different isotropic strains. The optical branches have been
			made more transparent to emphasis the behavior in the TA$_1$ and
			TA$_2$ branches. The color indicates direction from compressive
			to tensile strain. Note that the strain percent shown is with
			respect to isotropic changes (i.e. volume).  }
		\label{fig:mutter_zhong_ko_phonon_b2}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_M3GNet_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_CHGNet_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_MACE_B2_StrainsPhononBandstructure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) M3GNet,
			(middle) CHGNet, and (bottom) MACE potentials for different
			isotropic strains. Similar transcparency is used as done in
			\ref{fig:mutter_zhong_phonon_b2}.  }
		\label{fig:gnn_phonon_b2}
	\end{centering}
\end{figure}
